---
title: "Cyclistic Case Study"
author: "Jeff Bai"
date: '2022-07-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This case study is the capstone project for the Google Data Analytics Professional Certificate. The following analysis was completed for Course 8 - Case Study 1. 

## About Cyclistic

Cyclistic is a bike-share program founded in 2016 in Chicago, Illinois. Today, it operates more than 5,800 bicycles and 600 docking stations. With a variety of regular and assistive bike types (recumbents, hand-trikes, cargo bikes) and flexible pricing plans, Cyclistic has garnered broad appeal across consumer segments.

## Scenario

The director of marketing at Cyclistic, Lily Moreno, believes that the future success of the company depends on maximizing the number of annual memberships. To that end, our team wants to understand how casual riders and annual members use Cyclistic bikes differently. From there, Cyclistic will design a new marketing strategy to convert more casual riders into annual members.

## Business Task

We aim to answer three main guiding questions for the Cyclistic marketing team:

* How do annual members and casual riders user Cyclistic bikes differently?
* Why would casual riders buy Cyclistic annual memberships?
* How can Cyclistic use digital media to influence casual riders to become members?

## Data Sources

This analysis uses the [dataset](https://divvy-tripdata.s3.amazonaws.com/index.html) originally published in "'Sophisticated, Clear, and Polished': Divvy and Data Visualization (Case Study)" by Kevin Hartman. These data are used in this analysis under the terms of Motivate International's [Data License Agreement](https://ride.divvybikes.com/data-license-agreement).


## Setting up the R environment

For this analysis, we will be using R.

Set up the tidyverse:

```{r}
install.packages("tidyverse")
library(tidyverse)
```



## to be deleted
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
