---
title: "Cyclistic Case Study - How Does a Bike-Share Navigate Speedy Success?"
author: "Jeff Bai"
date: '2022-07-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This case study is the capstone project for the Google Data Analytics Professional Certificate. The following analysis was completed for Course 8 - Case Study 1. 

# Overview
### About Cyclistic
Cyclistic is a bike-share program founded in 2016 in Chicago, Illinois. Today, it operates more than 5,800 bicycles and 600 docking stations. With a variety of regular and assistive bike types (recumbents, hand-trikes, cargo bikes) and flexible pricing plans, Cyclistic has garnered broad appeal across consumer segments.

### Scenario
The director of marketing at Cyclistic, Lily Moreno, believes that the future success of the company depends on maximizing the number of annual memberships. To that end, our team wants to understand how casual riders and annual members use Cyclistic bikes differently. From there, Cyclistic will design a new marketing strategy to convert more casual riders into annual members.

### Stakeholders
**Lily Moreno, Director of Marketing**  
Develops campaigns and initiatives to promote the bike-share program.

**Cyclistic Marketing Analytics Team**  
Collects, analyzes, and reports data to guide Cyclistic's marketing strategy.

**Executive Team**  
Decides whether to approve the recommended marketing program.

### Data Sources
This analysis uses the [dataset](https://divvy-tripdata.s3.amazonaws.com/index.html) originally published in "'Sophisticated, Clear, and Polished': Divvy and Data Visualization (Case Study)" by Kevin Hartman. These data are used in this analysis under the terms of Motivate International's [Data License Agreement](https://ride.divvybikes.com/data-license-agreement).

# Scope of Work
### Business Task
The team aims to answer three main guiding questions for the Cyclistic marketing team:

* How do annual members and casual riders user Cyclistic bikes differently?
* Why would casual riders buy Cyclistic annual memberships?
* How can Cyclistic use digital media to influence casual riders to become members?

### Deliverables
* A clear statement of the business task
* A description of all data sources used
* Documentation of any cleaning or manipulation of data
* A summary of the analysis
* Supporting visualizations and key findings
* Top three recommendations based on analysis

# Define the Business Task

### The Current Problem
Cyclistic's marketing strategy has so far been focused on building awareness and appealing to broad consumer segments. This was accomplished with flexible pricing plans (single-ride passes, full-day passes, and annual memberships). However, Cyclistic is no longer able to rely solely on this strategy as it reaches market saturation.

Based on findings from the finance team, marketing director Moreno believes that future revenue growth is best captured by maximizing the number of annual members. In addition, since casual riders are already aware of the Cyclistic program, Moreno believes there is a high chance of converting casual riders into members, given the right marketing strategy.

The marketing analytics team's primary goal, therefore, is to determine how annual and casual riders differ in their usage behavior, why casual riders would want to buy annual memberships, and how Cyclistic can leverage digital media to influence casual riders to become members.

### Stakeholder Expectations
**Executive Team**  
The executive team will expect to receive a high-level takeaway of the main data analysis insights, along with how these insights drive Cyclistic's future marketing strategy.

**Lily Moreno, Director of Marketing**  
The director of marketing will expect evidence to support her theory and proposed marketing strategy.

# Documentation: Data Cleaning and Manipulation
### Setting up the R environment
For this analysis, we will be using R in RStudio.

Set up the tidyverse:

```{r, eval = FALSE}
install.packages("tidyverse")

library(tidyverse)
```

To assist in data cleaning, install here, skimr, and janitor, and load them into the environment:

```{r, eval = FALSE}
install.packages("here")
install.packages("skimr")
install.packages("janitor")

library(here)
library(skimr)
library(janitor)
```

### Importing raw dataset
The scope of our analysis covers the last 12 months of available trip data.

We first import the data CSVs as data frames into RStudio:

```{r, eval = FALSE}
df_202106 <- read_csv("datasets/202106-divvy-tripdata.csv")
df_202107 <- read_csv("datasets/202107-divvy-tripdata.csv")
df_202108 <- read_csv("datasets/202108-divvy-tripdata.csv")
df_202109 <- read_csv("datasets/202109-divvy-tripdata.csv")
df_202110 <- read_csv("datasets/202110-divvy-tripdata.csv")
df_202111 <- read_csv("datasets/202111-divvy-tripdata.csv")
df_202112 <- read_csv("datasets/202112-divvy-tripdata.csv")
df_202201 <- read_csv("datasets/202201-divvy-tripdata.csv")
df_202202 <- read_csv("datasets/202202-divvy-tripdata.csv")
df_202203 <- read_csv("datasets/202203-divvy-tripdata.csv")
df_202204 <- read_csv("datasets/202204-divvy-tripdata.csv")
df_202205 <- read_csv("datasets/202205-divvy-tripdata.csv")
```

### Assessing Data Quality
To assess data quality, we used the ROCCC (reliable-original-comprehensive-current-cited) model.

