---
title: "Cyclistic Case Study"
author: "Jeff Bai"
date: '2022-07-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Case Study Overview

This case study is the capstone project for the Google Data Analytics Professional Certificate. The following analysis was completed for Course 8 - Case Study 1.

## About Cyclistic

Cyclistic is a bike-share program founded in 2016 in Chicago, Illinois. Today, it operates more than 5,800 bicycles and 600 docking stations. With a variety of regular and assistive bike types (recumbents, hand-trikes, cargo bikes) and flexible pricing plans, Cyclistic has garnered broad appeal across consumer segments.

## Business Task

We aim to answer three main guiding questions for the Cyclistic marketing team:

* How do annual members and casual riders user Cyclistic bikes differently?
* Why would casual riders buy Cyclistic annual memberships?
* How can Cyclistic use digital media to influence casual riders to become members?

## Data Sources

This analysis uses the [dataset](https://divvy-tripdata.s3.amazonaws.com/index.html) originally published in "'Sophisticated, Clear, and Polished': Divvy and Data Visualization (Case Study)" by Kevin Hartman. These data are used in this analysis under the terms of Motivate International's [Data License Agreement](https://ride.divvybikes.com/data-license-agreement).


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
